Experiences with Planning for Natural Language Generation

### 2008-07-24 trunk/Papers/experiences/conclusion.tex
new graphs; small changes to acknowledgements

\paragraph{Acknowledgments.} This work is a collaboration that arose
in the context of the ``planning and language'' group at the
University of Edinburgh.  We thank all members of this group,
especially Hector Geffner and Mark Steedman, for interesting
discussions.  This work was supported by the DFG Research Fellowship
``CRISP: Efficient integrated realization and microplanning'' and the
EU project XYZ PACO-PLUS.

>>>>

\section{Acknowledgements}
This work arose in the context of the Planning and Language Interest Group
at the University of Edinburgh. We thank all members of this group,
especially Hector Geffner and Mark Steedman, for interesting discussions.
This work was partially supported by the DFG Research Fellowship ``CRISP:
Efficient integrated realization and microplanning'' and by the European
Commission through the PACO-PLUS project (FP6-2004-IST-4-27657).

%\paragraph{Acknowledgments.} This work is a collaboration that arose
%in the context of the ``planning and language'' group at the
%University of Edinburgh.  We thank all members of this group,
%especially Hector Geffner and Mark Steedman, for interesting
%discussions.  This work was supported by the DFG Research Fellowship
%``CRISP: Efficient integrated realization and microplanning'' and the
%EU project XYZ PACO-PLUS.
